Comparing MTurk and the US Population's Occupational Diversity

### 2018-01-26 Manuscript.Rmd

```{r message = FALSE, warning = FALSE}
#The packages below will allow you to access "papaja", and if it fails, then try running all of the code at once. It should work then. 
require(devtools)
install_github("crsh/papaja")
library("papaja")
```
#Introduction
  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population (@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using). Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena (e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common) and by organizational behavior (OB) researchers to expand the OB literature (e.g., @yarkoni2015interactions).

@@

```{r,BLS, include=FALSE, results='asis'}
#Load packages
library(readr)
library(readxl)
library(data.table)

#Load datasets. Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively). The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category. The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset. The UGA dataset is a full dataset in the sense that it contains all individuals whose data are relevant for our investigation (i.e., participants hold a job that falls under a SOC classification) or not (i.e., they either do not work or work in a job falling outside the SOC classification system).

#Build the BLS Table.
##BLS data
BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")
###Rename rows and aggregate.
BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
BLS[11, 1] = "31-39 Service Occupations"
BLS[12, 1] = "31-39 Service Occupations"
BLS[13, 1] = "31-39 Service Occupations"
BLS[14, 1] = "31-39 Service Occupations"
BLS[15, 1] = "31-39 Service Occupations"
BLS[16, 1] = "41 Sales and Related Occupations"
BLS[17, 1] = "43 Office and Administrative Support Occupations"
BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
BLS[19, 1] = "47 Construction and Extraction Occupation"
BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
BLS[21, 1] = "51 Production Occupation"
BLS[22, 1] = "53 Transportation and Material Moving Occupation"
BLS[23, 1] = "55 Military Specific Occupations"
names(BLS) <- c("Var1","Var2","Var3")
BLS <- aggregate(.~Var1,BLS,sum)
###Data on the size of the military taken from the department of defense (http://us-military-branches.insidegov.com). 
BLS[13, 2] = "1350236"
names(BLS) <- c("Intermediate Aggregation Title", "Freq","RFreq")
BLS$Freq <- as.numeric(BLS$Freq)
tab <- transform(BLS, relative = prop.table(Freq))
BLS <- tab[c(1,4)]
names(BLS) <- c("Intermediate Aggregation Title","e")
```

>>>>

```{r message = FALSE, warning = FALSE}
#The packages below will allow you to access "papaja", and if it fails, then try running all of the code at once. It should work then. 
library("papaja")
```
#Introduction
  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population (@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using). Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena (e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common) and by organizational behavior (OB) researchers to expand the OB literature (e.g., @yarkoni2015interactions).

@@

```{r,BLS, include=FALSE, results='asis'}
#Load packages
library(readr)
library(readxl)
library(data.table)
library(openxlsx)

#Load datasets. Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively). The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category. The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset. The UGA dataset is a full dataset in the sense that it contains all individuals whose data are relevant for our investigation (i.e., participants hold a job that falls under a SOC classification) or not (i.e., they either do not work or work in a job falling outside the SOC classification system). 
#Build the BLS Table, but first establish a temp file.

# Download the file with download.file()
# Here is the URL.
download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
unzip("BLS2015.zip")
library(readxl)
national_M2015_dl <- read_excel("oesm15nat/national_M2015_dl.xlsx")
View(national_M2015_dl)

#Edit the code below such that the newly downloaded data aligns with the code below. You'll need to include relative percentages.

BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")
###Rename rows and aggregate.
BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
BLS[11, 1] = "31-39 Service Occupations"
BLS[12, 1] = "31-39 Service Occupations"
BLS[13, 1] = "31-39 Service Occupations"
BLS[14, 1] = "31-39 Service Occupations"
BLS[15, 1] = "31-39 Service Occupations"
BLS[16, 1] = "41 Sales and Related Occupations"
BLS[17, 1] = "43 Office and Administrative Support Occupations"
BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
BLS[19, 1] = "47 Construction and Extraction Occupation"
BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
BLS[21, 1] = "51 Production Occupation"
BLS[22, 1] = "53 Transportation and Material Moving Occupation"
BLS[23, 1] = "55 Military Specific Occupations"
names(BLS) <- c("Var1","Var2","Var3")
BLS <- aggregate(.~Var1,BLS,sum)
###Data on the size of the military taken from the department of defense (http://us-military-branches.insidegov.com). 
BLS[13, 2] = "1350236"
names(BLS) <- c("Intermediate Aggregation Title", "Freq","RFreq")
BLS$Freq <- as.numeric(BLS$Freq)
tab <- transform(BLS, relative = prop.table(Freq))
BLS <- tab[c(1,4)]
names(BLS) <- c("Intermediate Aggregation Title","e")
```
